---
title: "Test Projek"
author: "Rifka Canalisa Rahayu"
date: "1/12/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Projek Penilaian Pariwisata

## Library
```{r}
library(xml2)
library(rvest)
library(ggplot2)
library(dplyr)
library(dslabs)
library(tidyverse)
```


```{r}
alamatweb <-'https://www.tripadvisor.com/Attraction_Review-g186338-d187555-Reviews-The_British_Museum-London_England.html'
lamanweb <- read_html(alamatweb)
```

# Judul review
```{r}
title_data_laman <- html_nodes(lamanweb,'.ocfR3SKN span span') 
title_data <- html_text(title_data_laman)
title_data <- as.character(title_data)
head(title_data)
```

# rating review
```{r}
rating_data_laman <- html_nodes(lamanweb,'.nf9vGX55') 
print(rating_data_laman)
rating_data <- gsub("\\D+", "", rating_data_laman)
rating_data <- substr(rating_data, 4, 4)
rating_data <- as.numeric(rating_data)
print(rating_data)
```

# Comment/Isi review
```{r}
comment_data_laman <- html_nodes(lamanweb,'.cPQsENeY q') 
comment_data <- html_text(comment_data_laman)
comment_data <- as.character(comment_data)
print(comment_data)

```

# Date Trip
```{r}
date_trip_laman <- html_nodes(lamanweb, '._34Xs-BQm ')
date_trip <- html_text(date_trip_laman)
date_trip <- substring(date_trip,21)
date_trip <- as.vector(date_trip)
print(date_trip)
```

# Reviewer Username
```{r}
user_laman <- html_nodes(lamanweb, '._2fxQ4TOx a ')
user <- html_text(user_laman)
user <- as.character(user)
print(user)
```

# Day write review
```{r}
day_laman <- html_nodes(lamanweb, '._2fxQ4TOx span ')
day <- html_text(day_laman)
day <- gsub("([^:]+). ([review])", "", day)
day <- substring(day, 7)
day <- as.vector(day)
print(day)
```


```{r}
data_review_museum <- data.frame(title = title_data, comment = comment_data, trip = date_trip, writer = user, 
                                 written = day, rating = rating_data)
str(data_review_museum)
```
data_review_museum <- data.frame(title = title_data, comment = comment_data, rating = rating_data)

```{r}
jumlah = 2500

if(jumlah > 5){
  if(jumlah %% 5 !=0){
    banyak_data = jumlah + (5 - (jumlah %% 5)) - 5
  } else{
    banyak_data = jumlah - 5
  }
  for (i in seq(from <- 5, to <- banyak_data, by = 5)){
   
      link = paste0("https://www.tripadvisor.com/Attraction_Review-g186338-d187555-Reviews-or",
                 i,"-The_British_Museum-London_England.html#REVIEWS")
      page = read_html(link)
      
      titles_data <- page %>% html_nodes('.ocfR3SKN span span') %>% html_text() 
      titles_data <- as.character(titles_data)
      
      comments_data <- page %>% html_nodes('.cPQsENeY q') %>% html_text() 
      comment_datas <- as.character(comments_data)
      
      users_data <- page %>% html_nodes('._2fxQ4TOx a ') %>% html_text()
      users_datas <- as.character(users_data)
      
      date_trips <- page %>% html_nodes('._34Xs-BQm ') %>% html_text()
      date_data <-  date_trips %>% substring(21) %>% as.vector()
      
      rates_data <- page %>% html_nodes('.nf9vGX55')
      rating_datas <- gsub("\\D+", "", rates_data) 
      rate_datas <- rating_datas %>% substr(4, 4) %>% as.numeric()
      
      days_data <- page %>% html_nodes('._2fxQ4TOx span ') %>% html_text()
      write_data <- gsub("([^:]+). ([review])", "", days_data)
      written_data <- write_data %>% substring(7) %>% as.vector()
      
      data_review_museum <- rbind(data_review_museum, 
                                  data.frame(title = titles_data, comment = comment_datas,  trip = date_data,
                                             writer = users_datas, written = written_data, rating = rate_datas ))
  }
}


```

```{r}
str(data_review_museum)
tail(data_review_museum)
```
```{r}
write.csv(data_review_museum ,"Data_Review_British_Museum.csv",row.names = F, fileEncoding = "UTF-8")
getwd()
```

